%-------------------------------------
% Resum in LaTeX (XeLaTeX)
% Author:  HF Yuan
% Project: https://github.com/xyz-yuanhf/yuan-resume
% Base on: https://github.com/mattyHerzig/mattys_resume
%          http://www.jianxu.net/en/
% License: MIT
%------------------------------------

\documentclass[a4paper, 10pt]{article}
\usepackage{myresume}  % Style package
\usepackage{xcolor}
\usepackage[hidelinks]{hyperref}
% --------------------  START  --------------------
\begin{document}

% -------------------- HEADING --------------------
\begin{flushright}
  \setstretch{0.6}
  \item {\Calluna (+39) 351-955-5147}  % Phone number
  \item {\Calluna \href{mailto:moein.taherinezhad@mail.polimi.it}{\textcolor{gray}{moein.taherinezhad@mail.polimi.it}}  % E-mail address
  \item {\Calluna \href{https://github.com/MoeinDSP}{\textcolor{gray}{GitHub} }  % Home page
\end{flushright}\vspace{-35pt}

\begin{flushleft}  % Replace here with your name (and identity if required)
  {\Calluna \fontsize{20pt}{20pt}\selectfont \textsc{Moein Taherinezhad}} \quad {\Calluna \fontsize{14.5pt}{14.5pt}\selectfont \textsc{M.Sc.}}
  \noindent\rule{\textwidth}{0.4pt}
\end{flushleft}

% -------------------- EDUCATION --------------------
\sectionBlock{
\section{Education}
}{
\eduHeading
  {Politecnico di Milano}{Milan, Italy}
  {M.Sc. in Telecommunication Engineering}{Sep. 2023 - Jan. 2026 \footnotesize{\textit{(expected)}}}
\itemListStart
  \myItem{GPA: 27.00/30.00}
  
\itemListEnd

\eduHeading
  {Semnan University}{Semnan, Iran}
  {B.E. in Electrical Engineering (Major in Telecommunication)}{Sep. 2018 - Jan. 2023}
\itemListStart
  \myItem{GPA: 18.09/20.00}
  \myItem{Designing a wearable planar antenna in the terahertz frequency band and optimizing its parameters to reduce SAR level (19.50/20.0)}{Supervisor: {\href{https://scholar.google.com/citations?user=kj6yG2YAAAAJ&hl=en}{\textcolor{gray}{Professor Pejman Rezaei}}}}
\itemListEnd

}

% -------------------- Research Interests -------------
\sectionBlock{
\section{Research Interests}
}{
\researchList
\justifying
\item \emph{Software Defined Networks}
\item \emph{Radio Access Network}: Open-RAN, RAN Intelligent Controller, 5G/
6G
\item \emph{Internet of Things (IoT)}
\item \emph{Network Measurement}
\item \emph{Cloud Computing}
\item \emph{Artificial Intelligence}: Machine Learning, Deep Learning
\researchListend
}


% ------------------- Technical Expertise --------------
\sectionBlock{
\section{Technical Expertise}
}{
\techList
\justifying
\item \emph{Programming Languages}: Python, C++, P4, MATLAB, Bash script
\item \emph{Development Infrastructure}: Docker, Kubernetes
\item \emph{AI Libraries}: Pytorch, Tensorflow, Scikit-learn
}



% -------------------- PUBLICATIONS --------------------
\sectionBlock{
\section{Publications}
}{
\pubListStart
\justifying
\item \textbfHR HR Heidari, P Rezaei, S Kiani, M Taherinezhad. \href{https://scholar.google.com/citations?user=sh-KHmUAAAAJ&hl=en}{\textcolor{gray}{A monopulse array antenna based on SIW with circular polarization for using in tracking systems.} \textit{AEU-International Journal of Electronics and Communications 162, 154563}}, \hfill 2023

\pubListEnd
}

% -------------------- PROJECTS --------------------
\sectionBlock{
\section{Projects}
}{
\pubListStart
{\textbf{Implementation of an O-RAN xApp and test it on real hardware}\hfill{Aug. 2024 - Present}}\newline
{\textcolor{gray}{\href{https://github.com/MoeinDSP/gNB-e2sm-emu}{Software defined gNB, }
\href{https://github.com/MoeinDSP/xapp-e2ap-py/tree/mrn-base}{RAN data collection/control through xApps, }
\href{https://github.com/MoeinDSP/oai-oran-protolib}{Protocol design, }
O-RAN, concepts and architecture, 
5G software development, 
Software Defined Radio, 
Manage over-the-air radio experiments and hardware equipment}}


{\textbf {\href{https://github.com/MoeinDSP/Optical-Failure-Localization} {Optical-Failure-Localization}}\hfill{May. 2024}}\newline

{\textbf {\href{https://github.com/MoeinDSP/Traffic-Prediction} {Traffic Prediction}}\hfill{May. 2024}}\newline

{\textbf {\href{https://github.com/MoeinDSP/Qualityof-Transmission-QoT-estimationin-opticalnetworks} {Quality of Transmission Estimation}}\hfill{Apr. 2024}}\newline


{\textbf{\href{https://github.com/MoeinDSP/Application-Flow-Identification}{Application Flow Identification}} \hfill{Apr. 2024}}\newline

{\textbf{\href{https://github.com/MoeinDSP/MAC-address-derandomization}{MAC address derandomization }} \hfill{ Mar. 2024}}\newline

{\textbf{\href{https://github.com/MoeinDSP/Round-Trip-Time-Analysis-}{Round-Trip-Time-Analysis}} \hfill{Mar. 2024}}\newline

{\textbf{\href{https://github.com/MoeinDSP/Websitefingerprinting}{Website fingerprinting}} \hfill{Feb. 2024}}
\pubListEnd
}\newline
% -------------------- AWARDS & HONORS --------------------
\sectionBlock{
\section{Awards\\and\\Honors}
}{
\awardListStart
\justifying
\item \emph{Awarded a merit-based scholarship}\newline Admitted to Universidad Politécnica de Madrid Erasmus Exchange student \hfill Apr. 2024 

\item \emph{Ranked 2\textsuperscript{nd} among 106 students, Talent student in faculty of Electrical and\newline Computer Engineering, Semnan University}\hfill Feb. 2023\newline Issued by Vice-Chancellor of Academic and Graduate Studies of Semnan University.

\awardListEnd
}
% -------------------- Work Experiences --------------------
\sectionBlock{
\section{Work Experiences}
}{

{\textbf{
  {Laboratory assistant in Antenna Design laboratory under Supervision of \href{https://scholar.google.com/citations?user=kj6yG2YAAAAJ&hl=en}
  {\textcolor{gray}{Dr. Pejman Rezaei}}}}\hfill{Sep. 2022 - Jan. 2023}\newline
}

{\textbf{
  {Laboratory assistant in digital communication laboratory under Supervision of \href{https://scholar.google.com/citations?user=GHJY61wAAAAJ&hl=en}
  {\textcolor{gray}{Dr. Ali Shahzadi}}}}\hfill{Sep. 2022 - Jan. 2023}\newline
}

{\textbf{
  {Research Assistant: \href{https://en.itrc.ac.ir/}{ICT Research Center, Ministry of ICT}}}\hfill{Sep. 2022 - Jan. 2023}\newline
Applying Machine Learning Algorithms in Wireless Communication Channel under the supervision of \href{https://scholar.google.ca/citations?user=fwtTUX0AAAAJ&hl=en}{\textcolor{gray}{Houman Zarrabi}}}
\newline

{\textbf{Teaching Assitant (Head TA)}
    
}{
    • Principle of Communication Systems, {\href{https://scholar.google.com/citations?user=GHJY61wAAAAJ&hl=en}{\textcolor{gray}{Dr. Ali Shahzadi}}}\hfill{Sep. 2021 - Jan. 2022}\neweline

    
    • Principle of Communication Systems, {\href{https://scholar.google.com/citations?user=GHJY61wAAAAJ&hl=en}{\textcolor{gray}{Dr. Ali Shahzadi}}}\hfill{Feb. 2021 - Jun. 2021}

     • Computer Programming, {\href{https://scholar.google.com/citations?user=zfvwqc0AAAAJ}{\textcolor{gray}{Dr. Razieh Rastgoo}}}\hfill{Feb. 2021 - Jun. 2021}

     • Signals and Systems, {\href{https://scholar.google.com/citations?user=kj6yG2YAAAAJ&hl=en}{\textcolor{gray}{Dr. Pejman Rezaei}}}\hfill{Feb. 2021 - Jun. 2021}

     • Engineering Mathematics, {\href{https://scholar.google.com/citations?user=kj6yG2YAAAAJ&hl=en}{\textcolor{gray}{Dr. Pejman Rezaei}}}\hfill{Sep. 2020 - Dec. 2020}

     • Engineering Mathematics, {\href{https://scholar.google.com/citations?user=kj6yG2YAAAAJ&hl=en}{\textcolor{gray}{Dr. Pejman Rezaei}}}\hfill{Feb. 2020 - Jun. 2020}\newline

}

{\textbf{Member of Electrical Engineering Scientific Student Community of Semnan University}

• Rank 1st among more than 50 Universities in a national competition
}\hfill{Jan. 2021}
}
\newline


%---------------------- Selected Courses ------------------------
\sectionBlock{
\section{Selected Courses}
}{
\courseListStarts
Internet of Things \hfill 30.0/30.0 \newline
Network Measurement Lab\hfill 28.0/30.0 \newline
Communication Network Design\hfill 27.0/30.0\newline
Game Theory\hfill 29.0/30.0\newline
Classical and Quantum error correction\hfill 30.0/30.0\newline
Wireless Internet\hfill 25.0/30.0\newline
Digital Communications\hfill 20.0/20.0\newline
Principles of Communication Systems\hfill 20.0/20.0\newline
Computer Networks\hfill 19.50/20.0\newline
Linear Algebra\hfill 19.70/20.0\newline
Microwave and Antenna\hfill 20.0/20.0\newline
Optical Communications\hfill 20.0/20.0\newline
Wireless Communication\hfill 20.0/20.0\newline
Field and Waves\hfill 18.0/20.0\newline
Communication Circuits\hfill 18.0/20.0\newline
Artificial Intelligence\hfill 18.50/20.0\newline
}

\courseListEnd

% -------------------- Certificates ------------------
\sectionBlock{
\section{Certificates}
}{
\CertificateListStarts
{\textbf{
  {\href{https://hamrah.academy/certificate-view/11417?lang=en&type=pdf}
  {{Software-Defined Networks}}}}\newline
}
{\textbf{
    {\href{https://coursera.org/share/d5cc3ea96710169e24aee0bd144b30b3}{Wireless Communications for Everybody}}\newline
}
{\textbf{
{\href{https://coursera.org/share/9f10b933575bc557383e9e9de92653c5}{Linux Fundamentals}}
}}\newline
{\textbf{
{\href{https://coursera.org/share/4c6768ce370238b313ea2797b750bd24}{Mathematics for Machine Learning and Data Science}}\newline
}}
{\textbf{
{\href{https://coursera.org/share/759d1eb0c39194ca375c3bb2bcf0ea1a}{Mathematics for Machine Learning: Linear Algebra}}
}}\newline
{\textbf{
{\href{https://coursera.org/share/902cf2a51eca66993808470fa45dfcc5}{Machine Learning}}
}}\newline
{\textbf{
{\href{https://coursera.org/share/c8f24b4073806dba1a0d949cd3bb2e8f}{Digital Signal Processing 1: Basic Concepts and Algorithms}}
}}\newline
{\textbf{
{\href{https://coursera.org/share/6efd6b5e99df9f8ea47b53868ff595fc}{Digital Signal Processing 2: Filtering}}
}}\newline
}}\newline
\CertificateListEnd
% -------------------- SKILLS --------------------
\sectionBlock{
\section{Language}
}{
\skillListStart
\justifying
\item  • English: TOEFL iBT (Test Score: 93)
\item  • Persian: Native
\skillListEnd
}

\end{document}

